Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-22 doc/mc-paper.tex
checkable POG --> certified POG

This paper introduces \emph{Partitioned-Operation Graphs} (POGs),
a generalization of the representations produced by current knowledge
compilers. The CPOG (for ``checkable'' POG) file format then
captures both the structure of a POG
and a checkable proof of its logical equivalence to a Boolean formula in
conjunctive normal form (CNF).  A CPOG
proof consists of a sequence of clause addition and deletion steps,
based on an extended resolution proof system~\cite{Tseitin:1983}.
We establish a set of conditions that, when satisified by a CPOG file, guarantee that it
encodes a well-formed POG and provides a valid equivalence proof.

>>>>

This paper introduces \emph{Partitioned-Operation Graphs} (POGs),
a generalization of the representations produced by current knowledge
compilers. The CPOG (for ``certified'' POG) file format then
captures both the structure of a POG
and a checkable proof of its logical equivalence to a Boolean formula in
conjunctive normal form (CNF).  A CPOG
proof consists of a sequence of clause addition and deletion steps,
based on an extended resolution proof system~\cite{Tseitin:1983}.
We establish a set of conditions that, when satisified by a CPOG file, guarantee that it
encodes a well-formed POG and provides a valid equivalence proof.
